INTELLIGENT SYSTEMS

### 2021-04-03 paper_4.tex
finish 4.4.1

\subsubsection{Recommendations for Evaluating CC Algorithm Performance}
In order to evaluate the performance of the algorithm with this type of 
dataset, it is recommended to use the following strategies:
\begin{enumerate}
    \item \emph{Camera independence}: the article proposes six-fold cross validation, 
    where each fold, divided into training, validation and test, contains a 
    grouping of images for each of the nine cameras. This technique aims 
    to obtain a fair evaluation of camera-independence of an algorithm (the 
    algorithm considers all images as if coming from the same camera).
    \item \emph{Camera and Scene Independence}: in this case it is recommended to 
    use the images acquired by Nikon and the mobile for training, while 
    the Canon images must be used for validation. As for the test, it is 
    recommended to use the Canon images belonging to the second group 
    of images. In this way you can understand the influence of camera-
    independence. If you get a low error, which means that the algorithm 
    treats each scene (each made up of images captured by different cameras) 
    as if it had been captured entirely by a single camera, then at 
    this point you would get, in addition to independence of the camera, 
    the independence of the scene. This is a good result if it is achieved in 
    this type of dataset.
    \item \emph{Camera and Scene Independence from Single Camera}: in this strategy 
    it is suggested to use the images from the second group as training 
    and validation while using the images acquired by Nikon and the 
    mobile for testing. In this way we want to understand if the algorithm 
    obtains the camera/scene independence effect with images produced 
    by another different camera (Canon). If this technique were 
    used with the 1 (where a low error implies the achievement of the 
    camera-independence) then when new images of different origin would 
    be inserted, the error would be higher than that obtained in 1, this is 
    because the camera-independence it faces the old set of cameras and not 
    the new one. It is being said that thanks to the combination of these, 
    it is possible to have a targeted camera-independence and a targeted 
    scene-independence for each new camera.
    \item \emph{Testing the Effect of Color Shading}: if you were to use the images 
    of your mobile, to test their color shading correction (CS), you could 
    enclose them all in a test set. Images that cause a high error will be 
    those that have not undergone the correction process.
    \item \emph{Testing the Effect of Resolution}: color constancy can be easily calculated 
    when the images are at high resolution. As you can guess, this 
    result is not achievable with images from a mobile phone. For this 
    reason, the dataset contains a portion of image downscaling (1080p) 
    useful for observing how the resolution can affect the performance of 
    the algorithm.
\end{enumerate}

@@

\subsubsection{Evaluation of a Direct Supervised Method}

>>>>

\subsubsection{Recommendations for Evaluating CC Algorithm Performance}\label{recommend}
In order to evaluate the performance of the algorithm with this type of 
dataset, it is recommended to use the following strategies:
\begin{enumerate}
    \item \emph{Camera independence}: the article proposes six-fold cross validation, 
    where each fold, divided into training, validation and test, contains a 
    grouping of images for each of the nine cameras. This technique aims 
    to obtain a fair evaluation of camera-independence of an algorithm (the 
    algorithm considers all images as if coming from the same camera).
    \item \emph{Camera and Scene Independence}: in this case it is recommended to 
    use the images acquired by Nikon and the mobile for training, while 
    the Canon images must be used for validation. As for the test, it is 
    recommended to use the Canon images belonging to the second group 
    of images. In this way you can understand the influence of camera-
    independence. If you get a low error, which means that the algorithm 
    treats each scene (each made up of images captured by different cameras) 
    as if it had been captured entirely by a single camera, then at 
    this point you would get, in addition to independence of the camera, 
    the independence of the scene. This is a good result if it is achieved in 
    this type of dataset.
    \item \emph{Camera and Scene Independence from Single Camera}: in this strategy 
    it is suggested to use the images from the second group as training 
    and validation while using the images acquired by Nikon and the 
    mobile for testing. In this way we want to understand if the algorithm 
    obtains the camera/scene independence effect with images produced 
    by another different camera (Canon). If this technique were 
    used with the 1 (where a low error implies the achievement of the 
    camera-independence) then when new images of different origin would 
    be inserted, the error would be higher than that obtained in 1, this is 
    because the camera-independence it faces the old set of cameras and not 
    the new one. It is being said that thanks to the combination of these, 
    it is possible to have a targeted camera-independence and a targeted 
    scene-independence for each new camera.
    \item \emph{Testing the Effect of Color Shading}: if you were to use the images 
    of your mobile, to test their color shading correction (CS), you could 
    enclose them all in a test set. Images that cause a high error will be 
    those that have not undergone the correction process.
    \item \emph{Testing the Effect of Resolution}: color constancy can be easily calculated 
    when the images are at high resolution. As you can guess, this 
    result is not achievable with images from a mobile phone. For this 
    reason, the dataset contains a portion of image downscaling (1080p) 
    useful for observing how the resolution can affect the performance of 
    the algorithm.
\end{enumerate}

@@

\subsubsection{Evaluation of a Direct Supervised Method}
In order to be able to calculate color constancy, and thus be able to achieve 
the camera-independence, various methods were used that included the use 
of convolutional neural networks (CNNs). In method \cite{0807099122}, the network used 
is composed of a convolutional layer with 240 filters of size 1x1, the usual 
function of ReLU, a max-Pooling of blocks of size 8x8 with stride 8. Finally 
there is a fully-connected layer with 40 layers hidden and a 3-dimensional 
output in which there is the estimated chromaticity of the lighting. In order to demonstrate the validity of the proposed dataset, the use of CNN has been adapted to the techniques described in \ref{recommend}:
\begin{enumerate}
    \item Following technique 1, various CNNs are trained to provide the least 
    possible error. The error reached by the model is less than when using 
    the Canon for training and validation. This means that the networks 
    assume the camera-independence only with the Nikon and mobile models. 
    Therefore the networks would be able to recognize new cameras. As 
    can be seen in the figure, the RAE values between the various cameras 
    are very similar (Fig. \ref{fig:CNNtec1}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper4/CNNtec1.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} with CCM on $ 1^{rst} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec1}
    \end{figure}
    \item Now a CNN is trained using technique 2. The training is carried out 
    with images acquired from both Nikon and mobile. Canon's images are 
    used for validation, while Canon's images belonging to the $ 2^{nd} $ field 
    are used for the test. Low errors are obtained with the use of a color 
    conversion matrix (CCM) \cite{0807099129} and therefore the model manages to have 
    the camera/scene-independence (Fig. \ref{fig:CNNtec2}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec2.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} with CCM on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec2}
    \end{figure}
    \item According to technique 3, a CNN can be trained to reach camera independence 
    only on one camera, excluding the others. In this case, since 
    the images of the $ 2^{nd} $ field, used for both training and validation, belong 
    only to Canon, then CNN will get the camera/scene-independence 
    only on this type of camera.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec3.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec2}
    \end{figure}
\end{enumerate}
